The Impact of Seasonal Changes on Mortality Rates in Toronto

### 2024-09-27 paper/paper.qmd
Upload - paper

```{r}
#| echo: false
#| eval: true
#| label: tbl-cleaned_death_registry_data
#| tbl-cap: "Sample Data"
#| warning: false

@@

@@

Our results are summarized in @tbl-modelresults.

>>>>

```{r}
#| echo: false
#| eval: true
#| label: tbl-cleaned_death_registry_data
#| tbl-cap: "Sample Cleaned Data"
#| warning: false

@@

## Summarized Data

```{r}
#| echo: false
#| eval: true
#| label: tbl-summerized_data
#| tbl-cap: "Summarized Data"
#| warning: false
#| tbl-subcap: ["Total Death toll by Season (2011-2023)", "Average Deaths by Month (2011-2023)"]
#| layout-ncol: 2

kable(total_deaths, col.names = c("Season", "Civic Centre", "Death Toll"))

kable(avg_death, col.names = c("Month", "Mean of the Death Toll"))
```

@@

Our results are summarized in @fig-deaths
Something
Something
Something
